\documentclass[12pt,a4paper]{article}

\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\usepackage{amsmath,amssymb}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{float}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{enumitem}
\usepackage{multirow}
\usepackage{array}

\title{Assignment \#1: Deep Neural Network for Regression and Deep Convolutional Neural Network for Classification}
\author{%
  Student Name \\
  Student ID \\[1em]
  COMP/EECE 7/8740 Neural Networks \\
  Spring 2026
}
\date{February 2026}

\begin{document}

% ---------------------------------------------------------------------------
% 1. Title Page
% ---------------------------------------------------------------------------
\maketitle
\thispagestyle{empty}
\newpage

% ---------------------------------------------------------------------------
% 2. Abstract
% ---------------------------------------------------------------------------
\begin{abstract}

\end{abstract}
\newpage

% ---------------------------------------------------------------------------
% 3. Introduction
% ---------------------------------------------------------------------------
\section{Introduction}

\subsection{Problem Definition}

\subsection{Background and Related Work}

\subsection{Objectives and Contributions}

% ---------------------------------------------------------------------------
% 4. Methodology
% ---------------------------------------------------------------------------
\section{Methodology}

\subsection{Overall System Pipeline}

\subsection{Data Preprocessing}

\subsection{Training and Testing Split}

\subsection{Evaluation Strategy}

% ---------------------------------------------------------------------------
% 5. Neural Network Model Descriptions
% ---------------------------------------------------------------------------
\section{Neural Network Model Descriptions}

\subsection{DNN Architecture for Regression (Task 1)}

* used LabelEncoder to turn Country into a number. Should have used one-hot encoding for best results, but this is fine!
* used MinMaxScaler to normalize so that high-magnitude variables like GDP don't dominate the gradient updates
* used He initialization [citation needed!] for weights

\subsection{DCNN Architecture for Classification (Task 2)}

\subsection{Activation Functions}
% Standard (ReLU, GELU) vs. proposed custom activation function

\subsection{Optimization Techniques}
% SGD with momentum, Adam, Gradient Descent from scratch

\subsection{Loss Functions and Hyperparameters}

% ---------------------------------------------------------------------------
% 6. Experiments and Results
% ---------------------------------------------------------------------------
\section{Experiments and Results}

\subsection{Dataset Description}

\subsubsection{Life Expectancy Dataset (Task 1)}

* Notice the loss is lower for ridge, but the MSE is lower for Lasso. This is because the loss includes penalties, but the MSE is strictly test results. So ridge ``looks better'' in training with lower loss but performs worse.

\subsubsection{COIL-20 Dataset (Task 2)}

\subsection{Exploratory Data Analysis (Task 1)}
% Descriptive statistics and visualizations for GDP, BMI, Alcohol, Total Expenditure

\subsection{Training and Testing Performance}
% Training and validation loss curves, accuracy and convergence behavior

\subsection{Quantitative Evaluation Metrics}

\subsubsection{Task 1: Regression Metrics}
% MSE, MAE, RMSE, R^2, Adjusted R^2

\subsubsection{Task 2: Classification Metrics}
% Accuracy, Precision, Recall, F1-score, Confusion Matrix, ROC, Precision-Recall curves

\subsection{Comparative Analysis}

\subsubsection{Regularization Comparison (Task 1)}
% Lasso, Ridge, ElasticNet

\subsubsection{Activation Function Comparison (Task 2)}
% ReLU, GELU, Custom

\subsubsection{Optimizer Comparison (Task 2)}
% SGD with momentum vs. Adam

\subsubsection{Threshold Analysis (Task 2)}
% Performance without thresholding vs. confidence > 0.9

\subsection{Discussion of Results}
% Justify why Adjusted R^2 is smaller than R^2 (Task 1)

\subsection{Limitations and Challenges}

% ---------------------------------------------------------------------------
% 7. Conclusion and Future Work
% ---------------------------------------------------------------------------
\section{Conclusion and Future Work}

% ---------------------------------------------------------------------------
% 8. References
% ---------------------------------------------------------------------------
\newpage
\bibliographystyle{ieeetr}
\begin{thebibliography}{99}

\bibitem{ref1} % Add references here

\end{thebibliography}

% ---------------------------------------------------------------------------
% 9. Assistance Disclosure
% ---------------------------------------------------------------------------
\section{Assistance Disclosure}

I used Claude AI in VS Code extensively for this assignment. Namely, I used AI to help write, format, debug, and proofread LaTeX and Python notebooks. I also used AI to explain or summarize course concepts and for brainstorming.

% ---------------------------------------------------------------------------
% 10. Appendix
% ---------------------------------------------------------------------------
\newpage
\appendix
\section{Appendix}

\subsection{Network Hyperparameters}

\subsection{Additional Plots}

\subsection{Pseudocode}

\end{document}
